How economic, health and social factors affect life expectancy in developing countries?

### 2025-04-10 paper.Rmd
should be done

model_table <- data.frame(
  Variable = c("(Intercept)", "Infant Deaths", "HIV/AIDS", "GDP per Capita", 
               "Schooling", "Percentage Expenditure", "Alcohol (Negligible)"),
  Estimate = c(49.50, -0.002131, -0.6713, 7.542e-06, 1.701, 0.00109, -0.670),
  Std_Error = c(0.7476, 0.0009369, 0.01917, 5.514e-05, 0.06129, 0.0003605, 0.2859),
  T_Value = c(66.216, -2.274, -35.018, 0.137, 27.757, 3.025, -2.343),
  P_Value = c("< 2e-16", "0.02309", "< 2e-16", "0.89121", "< 2e-16", "0.00253", "0.01924")
)

# Generate a nicely formatted table
kable(model_table, digits = 4, align = "c",
      col.names = c("Variable", "Estimate", "Std. Error", "t Value", "Pr(>|t|)"))

@@

Hasan: Completed writing for section 1,2,3 and 6. Conducted research and constructed the research question.

Arshh: Wrote section 5, helped with interpretation of final model results and model transformations, conducted research and literature review, helped formulate research question and helped with formatting.

>>>>

model_table <- data.frame(
  Variable = c("(Intercept)", "Infant Deaths", "HIV/AIDS", "GDP per Capita", 
               "Schooling", "Percentage Expenditure", "Alcohol (Negligible)"),
  Estimate = c(49.50, -0.002131, -0.6713, 7.542e-06, 1.701, 0.00109, -0.670),
  Std_Error = c(0.7476, 0.0009369, 0.01917, 5.514e-05, 0.06129, 0.0003605, 0.2859),
  # T_Value = c(66.216, -2.274, -35.018, 0.137, 27.757, 3.025, -2.343),
  P_Value = c("< 2e-16", "0.02309", "< 2e-16", "0.89121", "< 2e-16", "0.00253", "0.01924")
)

# Generate a nicely formatted table
kable(model_table, digits = 4, align = "c",
      col.names = c("Variable", "Estimate", "Std. Error", "Pr(>|t|)"))

@@

Hasan: Wrote for section 1,2,3 and 6. Conducted research and constructed the research question. Created and interpreted key findings for Infant deaths, HIV/AIDs and health expenditure. Created policy recommendations.

Arshh: Contributed writing to Section 1, 2 and 3. Wrote section 5, helped with interpretation of final model results and model transformations, conducted research and literature review, helped formulate research question and helped with formatting
